Who Needs Privacy?

### 2018-12-19 results/analyses.RmD
- slight changes

# edit variables
d %<>% 
  mutate(
    male = 2 - SES.SEX,
    time = V9 - V8,
    id = 1:nrow(.)
    ) %>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
  rename(
    age = SES.AGE,
    inc = SES.JOB_2
  )

>>>>

# edit variables
d %<>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
  mutate_at(vars(V8, V9), funs(parse_datetime(., c("%d.%m.%Y %H:%M")))) %>% 
  mutate(
    male = 2 - SES.SEX,
    time = V9 - V8,
    id = 1:nrow(.)
    ) %>% 
  rename(
    age = SES.AGE,
    inc = SES.JOB_2
  )
